---
output: 
  github_document:
    toc: TRUE
    toc_depth: 2
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = T
)
```


# Part 0. Proposal

Proposing the {knitrExtra} package! ðŸ¦„ 
<!-- (typical package introduction write up; but actually aspirational) -->

The goal of {knitrExtra} is to make some of my favorite functionality a little more accessible and usable interactively (in RStudio, I'm pretty much piggy backing on Kelly Bodwin's vision and work on this - led the way as to how-to w/ rstudio API).




Without the package, we live in the effort-ful world that follows ðŸ‹:

``` 

# grabbing code from a chunk: 
knitr::knit_code$get("chunk_code_get_static") |> as.vector()

# getting the names of chunks:
knitr::knit_code$get() |> names()

# sending code from a chunk to a stand alone file
knitr::knit_code$get("chunk_code_get_static") |> 
  as.vector() |> 
  writeLines("R/chunk_code_get_static.R")

```

And *importantly*, we can't access chunk names from within a live .Rmd, or the code from chunks in the document we are working on.  But this kind of interactivity can be useful.
  
With the {knitrExtra} package, we'll live in a different world (ðŸ¦„ ðŸ¦„ ðŸ¦„) where the task is a snap ðŸ«° and interactivity is provided (from within RStudio IDE - Borrowing from Kelly Bodwin's approach in flair): 

Proposed API:

```

library(knitrExtra)

knitrExtra::chunk_code_get("chunk_code_get_static")

knitrExtra::chunk_names_get()

knitrExtra::chunk_to_r("chunk_code_get_static")

```



# Part I. Work out functionality  ðŸš§ âœ… 

First, a helper function from the lightparser

```{r parse_current_rmd}
parse_current_rmd <- function(){
  
    ed        <- rstudioapi::getSourceEditorContext()
    source    <- ed$contents
    
    tmp <- tempfile()
    writeLines(source, tmp)
    
    lightparser::split_to_tbl(tmp)

}    
```


```{r}
parse_current_rmd()  
```


```{r chunk_code_get}
#' Title
#'
#' @param chunk_name a character string with the name of the chunk of interest
#'
#' @return a vector of the code contained in the referenced chunk
#' @export 
#'
#' @examples
chunk_code_get <- function(chunk_name = "chunk_code_get"){
  
  rmd_df <- parse_current_rmd()
  
  chunk_info <- subset(rmd_df, rmd_df$label == chunk_name) 
  
  chunk_info[,"code"][[1]][[1]] |> as.vector()
  
}
```




## Try it out

If we knit our document we'll see that these functions work

```{r}
chunk_code_get("chunk_code_get")
```



# Return chunk names

First we just alias knitr::all_label() to a function that's named more in line with others in this package.  

```{r chunk_names_get}
#' Title
#'
#' @return
#' @export
#'
#' @examples
chunk_names_get <- function(){
  
  rmd_df <- parse_current_rmd()
  
  chunks_info <- subset(rmd_df, !is.na(rmd_df$label)) |> as.data.frame() 
  
  chunks_info[,"label"]
  
}
```

```{r}
chunk_names_get()

```


# Code from chunks to files


It is nice to be able to grab code from chunks and send them to files for the purpose of building packages from a single file like a readme.  `chunk_to_dir` exists for this purpose.  The defaults are that you are sending code from a package readme to an .R file in the R package folder. 



```{r chunk_to_dir}
#' Title
#'
#' @param chunk_name 
#' @param dir 
#' @param extension 
#'
#' @return
#' @export
#'
#' @examples
chunk_to_dir <- function (chunk_name, dir = "R/", extension = ".R") 
{
    for (i in 1:length(chunk_name)) {
        writeLines(
          paste(chunk_code_get(chunk_name = chunk_name[i]), 
            collapse = "\n"), 
          con = paste0(dir, "/", chunk_name[i], extension))
    }
}


chunk_to_r <- function(chunk_name){
  
  chunk_to_dir(chunk_name = chunk_name)
  
}


chunk_to_tests_testthat <- function (chunk_name) 
{
    chunk_to_dir(chunk_name = chunk_name, dir = "tests/testthat/")
}
```


```{r}
chunk_to_dir("chunk_to_dir")

```

Finally, functionality (and the implementation) that I'm uncertain about is  `chunk_variants_to_dir()`  This is an interesting meta programming solution, perhaps. 


```{r chunk_variants_to_dir}
chunk_variants_to_dir <- function (chunk_name, chunk_name_suffix = "_variants", 
                                   file_name = NULL, 
    dir = "R/", replace1, replacements1, replace2 = NULL, replacements2 = NULL, 
    replace3 = NULL, replacements3 = NULL, replace4 = NULL, replacements4 = NULL) {
    template <- chunk_code_get(chunk_name)
    script_contents <- c()
    if (is.null(file_name)) {
        file_name <- paste0(chunk_name, chunk_name_suffix, ".R")
    }
    for (i in 1:length(replacements1)) {
        template_mod <- stringr::str_replace_all(template, replace1, 
            replacements1[i])
        if (!is.null(replace2)) {
            template_mod <- stringr::str_replace_all(template_mod, 
                replace2, replacements2[i])
        }
        if (!is.null(replace3)) {
            template_mod <- stringr::str_replace_all(template_mod, 
                replace3, replacements3[i])
        }
        if (!is.null(replace4)) {
            template_mod <- stringr::str_replace_all(template_mod, 
                replace4, replacements4[i])
        }
        script_contents <- c(script_contents, template_mod)
    }
    writeLines(script_contents, paste0(dir, file_name))
}
```



# Part II. Packaging and documentation  ðŸš§ âœ… 

## Phase 1. Minimal working package

### Bit A. Created package archetecture, running `devtools::create(".")` in interactive session. ðŸš§ âœ…


```{r, eval = F}
# devtools::create(".") # Bit 1. 1X
### Bit 2a: dependencies to functions using '::' syntax to pkg functions 
usethis::use_package("rstudioapi") # Bit 2b: document dependencies
usethis::use_package("stringr") # Bit 2b: document dependencies
usethis::use_dev_package(package = "lightparser", remote = "ThinkR-open/lightparser")

chunk_names_get()
```

```{r}
chunk_to_r("parse_current_rmd")
chunk_to_r("chunk_code_get")
chunk_to_r("chunk_names_get")
chunk_to_r("chunk_to_dir")
chunk_to_r("chunk_variants_to_dir") 
```

```{r, eval = F}
# Bit 3: send code chunk with function to R folder
devtools::check(pkg = ".")  # Bit 4: check that package is minimally viable; document's as a pre-step
devtools::install(pkg = ".", upgrade = "never") # Bit 5: install package locally
usethis::use_lifecycle_badge("experimental") # Bit 6: add lifecycle badge
# Bit 7 (below): Write traditional readme
# Bit 8: Compile readme
# Bit 9: Push to githup
# Bit 10: listen and iterate
```


### Bit 7. Write traditional README that uses built package (also serves as a test of build). ðŸš§ âœ… 

The goal of the {xxxx} package is to ...

Install package with:

```
remotes::install_github("GithubCoolUser/mypacakge")
```

Once functions are exported you can remove go to two colons, and when things are are really finalized, then go without colons (and rearrange your readme...)

```{r, eval = F}
library(knitrExtra)  ##<< change to your package name here
knitrExtra::chunk_names_get()
knitrExtra::chunk_code_get("chunk_to_dir")
knitrExtra:::parse_current_rmd()


getNamespaceExports("knitrExtra")

```

## Phase 3: Settling and testing ðŸš§ âœ… 

### Bit A. Added a description and author information in the [DESCRIPTION file](https://r-pkgs.org/description.html) ðŸš§ âœ…

### Bit B. Added [roxygen skeleton](https://r-pkgs.org/man.html)? ðŸš§ âœ…

### Bit C. Chosen a [license](https://r-pkgs.org/license.html)? ðŸš§ âœ…

```{r, eval = F}
usethis::use_mit_license()
```


### Bit D. Settle on [examples](https://r-pkgs.org/man.html#sec-man-examples).  Put them in the roxygen skeleton and readme. ðŸš§ âœ…

### Bit E. Written formal [tests](https://r-pkgs.org/testing-basics.html) of functions and save to test that folders ðŸš§ âœ…


That would look like this...

```{r test_calc_times_two_works, eval = F}
library(testthat)

test_that("calc times 2 works", {
  expect_equal(times_two(4), 8)
  expect_equal(times_two(5), 10)
  
})
```


```{r, eval = F}
readme2pkg::chunk_to_tests_testthat("test_calc_times_two_works")
```




### Bit F. Check again. Addressed notes, warnings and errors. ðŸš§ âœ…


```{r, eval = F}
devtools::check(pkg = ".")
```

## Phase 4. Promote to wider audience...  ðŸš§ âœ… 

### Bit A. Package website built? ðŸš§ âœ…


### Bit B. Package website deployed? ðŸš§ âœ…

## Phase 5: Harden/commit: Submit to CRAN/RUniverse ðŸš§ âœ… 

# Appendix: Reports, Environment

## Description file complete?  ðŸš§ âœ…

```{r, eval = F}
readLines("DESCRIPTION")
```

## Environment  ðŸš§ âœ…

Here I just want to print the packages and the versions

```{r}
all <- sessionInfo() |> print() |> capture.output()
all[11:17]
```

## `devtools::check()` report

```{r, eval=F, error = T, results="hide", warning=F}
devtools::check(pkg = ".")
```

## Package directory file tree

```{r}
fs::dir_tree(recurse = T)
```



